From Reversible Programs to \\ Univalent Universes and Back

### 2021-07-04 Pi+/paper/ufin.tex
Revising section 4
sec 2 and a couple of macros etc

\noindent The denotation $\sem{c}$ of a combinator $c : A \isot B$ is a path between $\sem{A}$ and $\sem{B}$. If the
size of $A$ is $m$ and the size of $B$ is $n$, the desired path is between $(\mathsf{Fin}~m, [ m , \mathsf{refl} ])$ and
$(\mathsf{Fin}~n, [ n , \mathsf{refl} ])$. This path is directly constructed using $\mathit{ap}$ and the fact that $m=n$
since combinators are always between types of the same size.

\noindent Finally, given two combinators $p , q : A \isot_1 B$ and a 2-combinator $\alpha : p \Iso q$, the denotation
$\sem{\alpha}$ of $\alpha$ is a path between $\sem{p}$ and $\sem{q}$.

>>>>

\noindent The denotation $\sem{c}$ of a combinator $c : A \isoone B$ is a path between $\sem{A}$ and $\sem{B}$. If the
size of $A$ is $m$ and the size of $B$ is $n$, the desired path is between $(\mathsf{Fin}~m, [ m , \mathsf{refl} ])$ and
$(\mathsf{Fin}~n, [ n , \mathsf{refl} ])$. This path is directly constructed using $\mathit{ap}$ and the fact that $m=n$
since combinators are always between types of the same size.

\noindent Finally, given two combinators $p , q : A \isoone B$ and a 2-combinator $\alpha : p \isotwo q$, the denotation
$\sem{\alpha}$ of $\alpha$ is a path between $\sem{p}$ and $\sem{q}$.
